### 2012-04-24 intention motor representation with corrado sinigaglia/intention and motor action.ppr.corrected.tex
a

Let us turn to motor representation. Compare imagining moving a ball with actually moving a ball.  To fully specify the comparison we intend, it is again necessary to distinguish two ways of imagining. One way of imagining action is phenomenologically something like acting except that such imaginings are not necessarily responsive to the features of actual objects and do not necessarily result in bodily movements. To illustrate suppose you are about to dive into a pool and, standing at the edge, mentally pantomime launching yourself from the bank. In some respects the experiences involved in this imaginative exercise may be barely distinguishable from experiences that might be involved in actually launching yourself into the pool. This way of imagining action can be distinguished from cognitive ways of imagining action which might involve thinking about an action.%
\footnote{
On distinguishing these two ways of imagining action, see \citet[p.\ 161]{currie:1997_mental}, \citet[p.\ 727]{jeannerod:1995_mental}, and \citet[p.\ 638-9]{kosslyn:2001_neural}. The former, phenomenologically action-like imagining is sometimes labelled `motor' or `internal' and occasionally identified by its links to motor processes or by features of the format or content of the representations involved (\citealp[p.\ 1400]{annett:1995_motor}). We avoid these labels because we introduce the distinction by appeal to phenomenology only and do not stipulate that motor representations are involved. It is essential for what follows that the involvement of motor representations in the phenomenologically action-like way of imagining action is a discovery rather than a stipulation.
}
The comparison we intend is between imagining moving a ball in the former, phenomenologically action-like way and actually moving a ball. There is evidence that the way imagining performing an action unfolds in time is similar in some respects to the way actually performing an action of the same type would unfold.  For instance, how long it takes to imagine moving an object is closely related to how long it would take to actually move that object \citep{decety:1989_timing, decety:1996_imagined, Jeannerod:1994oz}. In addition, for actions such as grasping the handle of a cup, manipulating the target object in ways that make the action harder (such as orienting the cup's handle to make it less convenient for you to grasp) make a corresponding difference to the effort involved in imagining performing the action \citep{parsons:1994_temporal, frak:2001_orientation}. Further, imagining performing an action can selectively interfere with performance of a related action. For example, suppose you are faced with an array of objects one of which---the target---you will shortly be required to grasp.  Subjects who imagine grasping an object other than the target object tend to be slower in subsequently grasping the target object than subjects who do not imagine acting or subjects who imagine grasping the target object \citep{ramsey:2010_incongruent_}. Just as the similarities between imagining seeing and actually seeing are evidence for the hypothesis that the representations involved in imagining seeing and actually seeing have a common format, so also the similarities in characteristic performance profile between imagining acting and actually acting, together with the particular patterns of interference between the two, suggest that imagining acting and actually acting involve a common representational format. And much as in the case of seeing and imagining seeing, acting and imagining acting involve many of the same processes almost up to the actual muscle contractions \citep{jeannerod:1995_mental, jeannerod:2003_mechanism}.

We have been comparing actually seeing with imagining seeing and actually acting with imagining acting as a first step towards arguing that visual and motor representations differ in format (which in turn will be background for an argument that motor representation and intention differ in format).  This claim could not easily be established by comparing actually seeing with actually acting because performance differences between these might be explained by bodily or environmental factors only distantly related to the representations involved. By contrast, comparing performance in imagining seeing and imagining acting does provide reasons to conclude that visual and motor representations differ in format. To see why, contrast imagining rotating a ball with imagining seeing a ball rotating.%
\footnote{Imagining acting without also imagining seeing may be difficult in practice, and conversely; it may also sometimes be difficult to distinguish imagining acting from imagining seeing \citep[as][p.\ 170 suggest]{currie:1997_mental}. However ordinary subjects can separate the two well enough to confirm predictions about their differences \citep[see, e.g.,][]{kosslyn:2001_imagining}.
}
As already mentioned, how quickly the former can be done is a function of how long it would take the agent to rotate the ball, whereas how quickly the latter can be done depends on how rapidly the ball can rotate and still be perceived as rotating. Similarly, we mentioned that factors making actually acting more effortful also make imagining acting more effortful. For instance, in some cases rotating a ball clockwise is easier than rotating it anti-clockwise, and so is imagining a ball rotate.  By contrast, the effort involved in actually seeing or imagining seeing a ball rotate does not similarly differ depending on direction.  These and other performance differences are plausibly a consequence of a difference in format between motor and visual representations.

>>>>

Let us turn to motor representation. Compare imagining moving a ball with actually moving a ball.  To fully specify the comparison we intend, it is again necessary to distinguish two ways of imagining. One way of imagining action is phenomenologically something like acting except that such imaginings are not necessarily responsive to the features of actual objects and do not necessarily result in bodily movements. To illustrate suppose you are about to dive into a pool and, standing at the edge, mentally pantomime launching yourself from the bank. In some respects the experiences involved in this imaginative exercise may be barely distinguishable from experiences that might be involved in actually launching yourself into the pool. This way of imagining action can be distinguished from cognitive ways of imagining action which might involve thinking about an action.%
\footnote{
On distinguishing these two ways of imagining action, see \citet[p.\ 161]{currie:1997_mental}, \citet[p.\ 727]{jeannerod:1995_mental}, and \citet[p.\ 638-9]{kosslyn:2001_neural}. The former, phenomenologically action-like imagining is sometimes labelled `motor' or `internal' and occasionally identified by its links to motor processes or by features of the format or content of the representations involved (\citealp[p.\ 1400]{annett:1995_motor}). We avoid these labels because we introduce the distinction by appeal to phenomenology only and do not stipulate that motor representations are involved. It is essential for what follows that the involvement of motor representations in the phenomenologically action-like way of imagining action is a discovery rather than a stipulation.
}
The comparison we intend is between imagining moving a ball in the former, phenomenologically action-like way and actually moving a ball. There is evidence that the way imagining performing an action unfolds in time is similar in some respects to the way actually performing an action of the same type would unfold.  For instance, how long it takes to imagine moving an object is closely related to how long it would take to actually move that object \citep{decety:1989_timing, decety:1996_imagined, Jeannerod:1994oz}. In addition, for actions such as grasping the handle of a cup, manipulating the target object in ways that make the action harder (such as orienting the cup's handle to make it less convenient for you to grasp) make a corresponding difference to the effort involved in imagining performing the action \citep{parsons:1994_temporal, frak:2001_orientation}. Further, imagining performing an action can selectively interfere with performance of a related action. For example, suppose you are faced with an array of objects one of which---the target---you will shortly be required to grasp.  Subjects who imagine grasping an object other than the target object tend to be slo wer in subsequently grasping the target object than subjects who do not imagine acting or subjects who imagine grasping the target object \citep{ramsey:2010_incongruent_}. Just as the similarities between imagining seeing and actually seeing are evidence for the hypothesis that the representations involved in imagining seeing and actually seeing have a common format, so also the similarities in characteristic performance profile between imagining acting and actually acting, together with the particular patterns of interference between the two, suggest that imagining acting and actually acting involve a common representational format. And much as in the case of seeing and imagining seeing, acting and imagining acting involve many of the same processes almost up to the actual muscle contractions \citep{jeannerod:1995_mental, jeannerod:2003_mechanism}.

We have been comparing actually seeing with imagining seeing and actually acting with imagining acting as a first step towards arguing that visual and motor representations differ in format (which in turn will be background for an argument that motor representation and intention differ in format).  This claim could not easily be established by comparing actually seeing with actually acting because performance differences between these might be explained by bodily or environmental factors only distantly related to the representations involved. By contrast, comparing performance in imagining seeing and imagining acting does provide reasons to conclude that visual and motor representations differ in format. To see why, contrast imagining rotating a ball with imagining seeing a ball rotating.%
\footnote{Imagining acting without also imagining seeing may be difficult in practice, and conversely; it may also sometimes be difficult to distinguish imagining acting from imagining seeing \citep[as][p.\ 170 suggest]{currie:1997_mental}. However ordinary subjects can separate the two well enough to confirm predictions about their differences \citep[see, e.g.,][]{kosslyn:2001_imagining}.
}
As already mentioned, how quickly the former can be done is a function of how long it would take the agent to rotate the ball, whereas how quickly the latter can be done depends on how rapidly the ball can rotate and still be perceived as rotating. Similarly, we mentioned that factors making actually acting more effortful also make imagining acting more effortful. For instance, in some cases rotating a ball clockwise is easier than rotating it anti-clockwise, 
%*correction!
and so is imagining rotating a ball.  By contrast, the effort involved in actually seeing or imagining seeing a ball rotate does not similarly differ depending on direction.  These and other performance differences are plausibly a consequence of a difference in format between motor and visual representations.
